%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
% \addbibresource{bibliography.bib}
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
% Specify the bibliography file to include publications
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\RequirePackage{fixltx2e}
\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage{rotating}

\usepackage{unicode-math}

\begin{document}


\header{rui}{Oliveira}{Software Engineer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{info}
Rui Pedro A. Oliveira
Portuguese, UE
1994.11.10
Male
\section{contact}
Rua São Martinho nº55
4765-343 V. N. Famalicão
Portugal
~
+(351) 915015377
~
\href{mailto:rui96pedro@gmail.com}{rui96pedro@gmail.com}
~
\href{http://ruioliveiras.eu}{http://ruioliveiras.eu}
~
\section{languages}
portuguese
english
\section{programming}
Scala, Java, C,
Akka,
Javascript,
Sql, NoSql (Couchchbase)
Git, Linux {\color{red} $\varheartsuit$}
~
\end{aside}

%---------------------------------------------------------------------------------------
%			Resumo
%---------------------------------------------------------------------------------------
\section{aboutMe}
I'm a programmer since 2010.
My first steps as a programmer was in the high school, in a programming course. The final project of this course are highlighted.
Continued the studies with BSc in Informatics Engineering.
To complete the education background I did a summer internship.
After completing the BSc started working as Full-Stack developer, developing Software as a Service.
In this project, also went to Web Summit 2016, making market prospection.

% Currently attending the 3rd year of the BSc in Informatics Engineering at Minho University (Braga, Portugal),
% after concluding a high school professional programming course. Throughout the BSc, the students are required
% to do several practical assignments, being some of them detailed in the portfolio below.
% The high school final project is also highlighted. In addition to a good educational background, a short term
% summer internship was held at the end of the 2nd year of study.

%Student of BSc in Informatics Engineering (some practical works on my Portfolio page)\\ High school: Professional course in programming (internship and final project).


%---------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%---------------------------------------------------------------------------------------
\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2015 2016}
{Impacting Group }
{Porto,Portugal}
{\emph{Software Engineer - Full-Stack Developer (1 year 7 months)} \\
% Development of Saas4saaS. Saas4saaS is a set of services to create Software as a service, the implemented services was User management and Subscription Management.
% I was responsible
% R\&D about the possibility of create a new product.
% Development of saas4saas, a project made in scala using Spray and Akka.
Research and development of Software as a Service:
\begin{itemize}
 \item Centralized Log Solution (working prototype)
 \item Centralized User management (Production ready)
 \item Subscription management (Production ready)
\end{itemize}
keywords: Java, Spring, Maven, Scala, Akka, Play, SBT, NoSQL (couchbase), Swagger,
}

\entry
{2014}
{Wondeotec - {\normalfont emailbidding.com}}
{Porto,Portugal}
{\emph{Summer Internship (2 months)} \\
Participation in the development of EmailBidding, a email marketing platform, made in Symfony2. Highlights: Php, Symfony2, team working with scrum and JIRA.
}

\entry
{2012}
{Codevision}
{Braga,Portugal}
{\emph{Professional Internship (2 months)} \\
Development of a mobile web application (Javascript - Sencha Touch framework, Visual Studio, MVC Architecture)
}
\end{entrylist}


%---------------------------------------------------------------------------------------
%			EDUCATION SECTION
%---------------------------------------------------------------------------------------
\section{education}

\begin{entrylist}
% LICENCIATURA------------------------------------------
\entry
{2012--2015}
{BSc in Informatics Engineering }
{University of Minho, Portugal}
{Comprehensive and prestiged undergraduate course in computer science and informatics engineering. Highlights: object-oriented, functional and imperative programming; Algorithms and data structures; Relational database architecture and management; Distributed Systems - concurrency and synchronization. Degree grade: 16 }
%CURSO PROFISSIONAL------------------------------------------
\entry
{2009--2012}
{Professional Course {\normalfont High School}}
{Didaxis, Portugal}
{\emph{Professional Course in Management and Programming of Computer Systems}. Highlights: introduction to C, .Net and Java programming languages. Final project: development of an Android Application (see below in awards). Internship: Codevision (see below in experience). Degree grade: 17}

%------------------------------------------------
\end{entrylist}


% --------
% New Page
% -------
\newpage
%-------------------------------------------------------------------------------------
%	AWARDS SECTION
%-------------------------------------------------------------------------------------
\section{other skills}
\begin{entrylist}
%------------------------------------------------
\entry
{2016}
{Market Prospection: Web Summit 2016}
{Lisbon, Portugal}
{I went to Web summit 2016 to get market feedback about the SaaS that we was creating in Impacting Group,}

\entry
{2014}
{Speaking: Php Introduction}
{University of Minho, Portugal}
{Workshop based course. Subjects: HTML, PHP and Laravel Framework.}

\entry
{2013}
{Entrepreneur: My Project is Entrepreneur}
{Municipal award, Vila Nova de Famalicão (Portugal)}
{Final project of the Professional Course, an Android application. It was winner of a entrepreneur conquest. }
% Android Application to manage people wardrobe.}
%------------------------------------------------
% \entry
% {2012}
% {TECLA (1\textsuperscript{st} place)}
% {Programming Competition, Aveiro (Portugal)}
% {TECLA is a programming competition for teams of two elements. The objective is to solve algorithmic challenges.}
%------------------------------------------------
\entry
{2011}
{Competitor: ONI (5\textsuperscript{th} place)}
{Programming Competition, Porto (Portugal)}
{ONI is the Portuguese National Olympiads of Informatics.}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

%\section{speaking}
%\begin{entrylist}
%    \entry
%    {2014}
%    {Php Introduction}
%    {University of Minho, Portugal}
%    {Workshop based course. Subjects: HTML, PHP and Laravel framework.}
%\end{entrylist}

\section{portfolio {\normalfont \normalsize (\href{https://bitbucket.org/ruioliveiras}{https://bitbucket.org/ruioliveiras})}}

\begin{entrylist}
% SEI
\entry
{2016}
{Personal Blog {\normalfont \normalsize (\href{http://ruioliveiras.eu}{http://ruioliveiras.eu})}}
{Porto, Portugal}
{
  I have done this blog using a static generator (HarpJS).
  I'm creating a Scala tutorial in the following link: \href{http://ruioliveiras.eu/post/scala-tutorial.html}{http://ruioliveiras.eu/post/scala-tutorial.html}
  % My blog is responsible, the side-menu in mobile collapse. And support a summary in the posts.
}

\entry
{2015}
{Musical challenge application Client/Server}
{University of Minho, Portugal}
{
    Application created with Java. Allows the existence of many inter-connected servers, with each client connecting to one server. Technical highlights:
\begin{itemize}
    \item Client/Server communication using UDP Datagrams
    \item Server/Server communication using TCP sockets
    \item UPD datagram fragmentation system
\end{itemize}
}


% SEI
% \entry
% {2014}
% {SEI 2015 web  {\normalfont \normalsize (\href{https://github.com/cesium/SEI15}{https://github.com/cesium/SEI15})}}
% {University of Minho, Portugal}
% {Participation in the development of SEI 2015 Web-Site. Implemented angularJS usage to avoid html repetitions.}

% distributed systems:
% \entry
% {2014}
% {Distributed System \"Warehouse\" Client/Server }
% {University of Minho, Portugal}
% {Client/Server made with Java using socket. Technical highlights:
% \begin{itemize}
%    \item Concurrency control with reentrant locks and conditions.
%    \item Communication inside sockets with pure text using serializing and deserializing.
% \end{itemize}
% }
% habitat application
\entry
{2014}
{CRUD management Application for Habitat Portugal}
{University of Minho, Portugal}
{CRUD management Application made with Java and MySql database. Technical highlights:
\begin{itemize}
    \item Three layers: View, Business, Data.
    \item Database with triggers
    \item Generic interface design
\end{itemize}
}
% Dpum
% \entry
% {2014}
% {Dpum CESIUM code validator}
% {University of Minho, Portugal}
% {Web site created to manage a programming conquest at Minho university.}

%------------------------------------------------

%\begin{itemize}
%	\item Login, using session token with time out;
%	\item Manage Items, Users, purchases;
%	\item Add pictures to items;
%\end{itemize}

%------------------------------------------------
\entry
{2013}
{C++ File Compressor, Shannon Fano algorithm}
{University of Minho, Portugal}
{Implementation highlights: % Graph based algorithms and Bitwise operations.
\begin{itemize}
  \item Graphs algorithms;
	\item Dynamic allocated memory;
	\item Bitwise operation;
\end{itemize}
}
%------------------------------------------------
\end{entrylist}


\end{document}
